### 2014-04-15 intro/intro.Rmd
some changes

pos = c(.1, .13, .15, .23, .25, .40, .44, .65, .76, .78, .81)
hgt = c(2, 3.6, 2, 5, 7.5, 6.9, 2, 4.8, 2, 4.1, 2.3)
wth = c(.005, .005, .006, .01, .01, .03, .01, .01, .005, .008, .005)
mu.b = rep(0,n)
for(j in 1:length(pos)){
  mu.b = mu.b + hgt[j]/(( 1 + (abs(t - pos[j])/wth[j]))^4)
}
dop.f=function(x) sqrt(x*(1-x))*sin((2*pi*1.05)/(x+0.05))
mu.dop=dop.f(t)

var1=1.42*((3-20*t)*(t>=0&t<0.1)+(20*t-1)*(t>=0.1&t<0.25)+(4+(1-4*t)*18/19)*(t>=0.25&t<0.725)+(2.2+10*(t-0.725))*(t>=0.725&t<0.89)+(3.85-85*(t-0.89)/11)*(t>=0.89&t<=1))
var2=(1+4*(exp(-550*(t-0.2)^2)+exp(-200*(t-0.5)^2)+exp(-950*(t-0.8)^2)))/1.35
var3=mu.b
var4=3.4*(2+mu.dop)

>>>>

pos = c(.1, .13, .15, .23, .25, .40, .44, .65, .76, .78, .81)
hgt = c(4, 5, 3, 4, 5, 4.2, 2.1, 4.3, 3.1, 5.1, 4.2)
wth = c(.005, .005, .006, .01, .01, .03, .01, .01, .005, .008, .005)
mu.b = rep(0,n)
for(j in 1:length(pos)){
  mu.b = mu.b + hgt[j]/(( 1 + (abs(t - pos[j])/wth[j]))^4)
}
dop.f=function(x) sqrt(x*(1-x))*sin((2*pi*1.05)/(x+0.05))
mu.dop=dop.f(t)

var1.ini=((3-20*t)*(t>=0&t<0.1)+(20*t-1)*(t>=0.1&t<0.25)+(4+(1-4*t)*18/19)*(t>=0.25&t<0.725)+(2.2+10*(t-0.725))*(t>=0.725&t<0.89)+(3.85-85*(t-0.89)/11)*(t>=0.89&t<=1))
var1=var1.ini/sqrt(var(var1.ini))
var2.ini=(1+4*(exp(-550*(t-0.2)^2)+exp(-200*(t-0.5)^2)+exp(-950*(t-0.8)^2)))
var2=var2.ini/sqrt(var(var2.ini))
var3=mu.b/sqrt(var(mu.b))
var4=(mu.dop+2)/sqrt(var(mu.dop))

### 2014-04-15 tests/tests.Rmd
some changes

```{r}
source(file.path("../Rcode/bayesmooth.R"))
spike.f=function(x) (0.75*exp(-500*(x-0.23)^2)+1.5*exp(-2000*(x-0.33)^2)+3*exp(-8000*(x-0.47)^2)+2.25*exp(-16000*(x-0.69)^2)+0.5*exp(-32000*(x-0.83)^2))

pos = c(.1, .13, .15, .23, .25, .40, .44, .65, .76, .78, .81)
hgt = 2.97/5*c(4, 5, 3, 4, 5, 4.2, 2.1, 4.3, 3.1, 5.1, 4.2)
wth = c(.005, .005, .006, .01, .01, .03, .01, .01, .005, .008, .005)
mu.b = rep(0,n)
for(j in 1:length(pos)){
  mu.b = mu.b + hgt[j]/(( 1 + (abs(t - pos[j])/wth[j]))^4)
}

@@

>>>>

```{r}
source(file.path("../Rcode/bayesmooth.R"))

spike.f=function(x) (0.75*exp(-500*(x-0.23)^2)+1.5*exp(-2000*(x-0.33)^2)+3*exp(-8000*(x-0.47)^2)+2.25*exp(-16000*(x-0.69)^2)+0.5*exp(-32000*(x-0.83)^2))

@@

pos = c(.1, .13, .15, .23, .25, .40, .44, .65, .76, .78, .81)
hgt = c(4, 5, 3, 4, 5, 4.2, 2.1, 4.3, 3.1, 5.1, 4.2)
wth = c(.005, .005, .006, .01, .01, .03, .01, .01, .005, .008, .005)
mu.b = rep(0,n)
for(j in 1:length(pos)){
  mu.b = mu.b + hgt[j]/(( 1 + (abs(t - pos[j])/wth[j]))^4)
}
